\begin{thebibliography}{99}

%
%cites from introduction
%

%
%cites from detbeamtest
%

\bibitem{dunecdr} "LBNF/DUNE Conceptual Design Report",  \url{https://web.fnal.gov/project/LBNF/ReviewsAndAssessments/LBNF-DUNE\%20CD-1-Refresh\%20Directors\%20Review/SitePages/Conceptual\%20Design\%20Report.aspx}

\bibitem{eoi} "Expression of Interest for a Full-Scale Detector Engineering Test and Test Beam Calibration of a Single-Phase LAr TPC" M.A. Leigui de Oliveira et al, SPSC-EOI-011, \url{http://cds.cern.ch/record/1953730/files/SPSC-EOI-011.pdf?version=1}

\bibitem{montanari_35ton} First scientific application of the membrane cryostat technology, D.Montanari et al, \textit{AIP Proceedings 1573, 1664 (2014)} \url{http://scitation.aip.org/content/aip/proceeding/aipcp/10.1063/1.4860907}

% Add if doc can be made public in docdb -- AH 
 \bibitem{montanari_35ton_perf} Performance And Results of the LBNE 35 ton Membrane Cryostat Prototype \textit{D.Montanari et al, 25th International Cryogenic Engineering Conference and the International Cryogenic Materials Conference in 2014, ICEC 25-ICMC 2014, LBNE Docid 9270} 

\bibitem{WA105} I. De Bonis et al. (The LBNO-DEMO (WA105) Collaboration), Technical Design Report for large-scale neutrino detectors prototyping and phased performance assessment in view of a long-baseline oscillation experiment, CERN-SPSC-TDR-004, arXiv:1409.4405 (2014)

\bibitem{CRubbia}"The Liquid-argon time projection chamber: a new concept for Neutrino Detector", C. Rubbia, CERN-EP/77-08 (1977).

\bibitem{icarus_mainref} "Design, construction and tests of the ICARUS T600 detector", ICARUS Collaboration, Nucl. Inst. Meth., A527 (2004) 329-410. 
%\bibitem{ICARUS2} 
"Performance of a liquid argon time projection chamber exposed to the CERN West Area Neutrino Facility neutrino beam", F. Arneodo et al. (ICARUS-Milano Collaboration) - Physical Review D (2006) (Vol. 74, No. 112001). 

\bibitem{argoneut1} "First Measurements of Inclusive Muon Neutrino Charged Current Differential Cross Sections on Argon." C. Anderson et al, Physical Review Letters (PRL) 108 (2012), 161802. 

\bibitem{argoneut2} "The ArgoNeuT Detector in the NuMI Low-Energy beam line at Fermilab" C. Anderson et al, Journal of Instrumentation (JINST), 2012 JINST Vol. 7 P10019. 

\bibitem{LArIAT} \url{http://intensityfrontier.fnal.gov/lariat.html}

\bibitem{captain} H. Berns et al. [The CAPTAIN Collaboration], arXiv:1309.1740 [physics.ins-det].

\bibitem{fluka05} "FLUKA: a multi-particle transport code" A. Ferrari, P.R. Sala, A. Fasso`, and J. Ranft, CERN-2005-10 (2005), INFN/TC\_05/11, SLAC-R-773.

\bibitem{miniboonefsi}  "Measurement of neutrino-induced charged-current charged pion production cross sections on mineral oil at E$\sim$1 GeV" A. A. Aguilar-Arevalo, et al., Phys. Rev. D 83, 052007 (2011).

\bibitem{minervafsi} "Charged Pion Production in Interactions on Hydrocarbon 
at $\overline{E}$= 4.0 GeV", B. Eberly et. al., arXiv:1406.6415 [hep-ex].

\bibitem{genie} "The GENIE Neutrino Monte Carlo Generator", C. Andreopoulos, et al., Nucl. Instrum. Meth. A614, 87 (2010).

\bibitem{fsirev} "Pion-nucleus Interactions", T.~S.~H. Lee and R. P. Redwine, Ann. Rev. Nucl. Sci,  {\bf 52}, 23 (2002).

\bibitem{jaffe} "The columnar theory of ionization", Ann. Phys. {\bf 42}, 303 (1931).

\bibitem{argoneut_angle} "A study of electron recombination using highly ionizing particles in the ArgoNeuT Liquid Argon TPC", 
R. Acciarri et al, Journal of Instrumentation 
(JINST), 2013 JINST Vol. 8 P08005.

\bibitem{icarus_recombination} "Study of electron recombination in liquid argon with the ICARUS TPC", S. Amoruso et. al, NIM A {\bf 523}, 275 (2004). 

\bibitem{nn_pid} "Neural Network Parameterizations of Electromagnetic Nucleon Form Factors", K. M. Graczyk, P. Plonski, R. Sulej, JHEP Vol. 2010, No 9, pp.1-30 (2010).

\bibitem{rd_pid} NetMaker, \url{http://www.ire.pw.edu.pl/~rsulej/NetMaker}

\bibitem{icarus_reco}
%spatial and calorimetric reconstruction algorithm is also published:
"Precise 3D track reconstruction algorithm for the ICARUS T600 liquid argon time projection chamber detector", ICARUS Collaboration, 
Adv.High Energy Phys., vol. 2013, p. 260820, 2013

\bibitem{icarus_eg} "Experimental search for the LSND anomaly with the ICARUS
detector in the CNGS neutrino beam", ICARUS Collaboration, Eur. Phys. J. C (2013) 73:2345.

\bibitem{argoneut_eg} "Results from and Status of ArgoNeuT and MicroBooNE" A. Szelc., XXVI International Conference on Neutrino Physics and Astrophysics (\url{http://neutrino2014.bu.edu/}).

\bibitem{stopmu} LBNE docdb~\#9079, \url{http://lbne2-docdb.fnal.gov/cgi-bin/ShowDocument?docid=9079}

\bibitem{bueno} "Nucleon Decay Searches with large Liquid Argon TPC Detectors at Shallow Depths: atmospheric neutrinos and cosmogenic backgrounds", A.Bueno, Z.Dai, Y.Ge, M.Laffranchi, A.J.Melgarejo, A.Meregaglia, S.Navas, A.Rubbia, JHEP 0704:041, (2007).

%
%cites from singlephasedet
%
  %
  %cites from singlephasedet input: APA-CP-FieldCage
  %
\bibitem{mat-test-stand} "A system to test the effects of materials on the electron drift lifetime in liquid argon and observations on the effect of water", R. Andrews, et al., Nucl. Instrum. Meth. A608 (2009) 251-258

\bibitem{LBNE-design} LBNF/DUNE Conceptual Design Report Annex 4A: The LBNE Design for a Deep Underground Single-Phase Liquid Argon TPC," LBNE-doc-10685 \url{http://lbne2-docdb.fnal.gov/cgi-bin/ShowDocument?docid=10685}

\bibitem{spacecharge} LBNE docdb~\#6471, \url{http://lbne2-docdb.fnal.gov/cgi-bin/ShowDocument?docid=6471}

\bibitem{CFD} LBNE docdb~\#6140, \url{http://lbne2-docdb.fnal.gov/cgi-bin/ShowDocument?docid=6140}

  %
  %cites from singlephasedet input: photondetector
  %



\bibitem{rayleigh} E. Grace, J. Nikkel,  arXiv: 1502.04213

\bibitem{absorption} B. Jones et al., arXiv: 1306.4605


\bibitem{rayleigh} E. Grace, J. Nikkel,  arXiv: 1502.04213

\bibitem{absorption} B. Jones et al., arXiv: 1306.4605

%\bibitem{conversio-eff}

\bibitem{sensl} SensL SiPM, \url{http://sensl.com/products/silicon-photomultipliers/cseries/}
  %
  %cites from singlephasedet input: readout
  %

  %
  %cites from singlephasedet input: daq
  %

%
%cites from cryo
%

\bibitem{sbnd} \url{http://sbn-nd.fnal.gov/}

% \bibitem{acciarri_sbn_proposal} A Proposal for a Three Detector Short-Baseline Neutrino Oscillation Program in the Fermilab Booster Neutrino Beam \textit{R.Acciarri et al} \url{http://arxiv.org/abs/1503.01520}

\bibitem{outgassing} R. Rebel et al., Journal of Physics: Conference Series {\bf 308} (2011) 012023; doi:10.1088/1742-6596/308/1/012023
%Outgassing reference based on Materials Test Stand (MTS) and the Liquid Argon Purity Demonstrator (LAPD)

%
%cites from calibration
%
%\bibitem{ref:space_charge} "Space charge effect at microBooNE" M. Mooney, X. Qian, C. Thorn,  B. Yu \url{http://microboone-docdb.fnal.gov/cgi-bin/RetrieveFile?docid=3983&filename=MicroBooNE_CollaborationMeeting_14_12_17.pdf&version=1}.

%
%cites from testbeamreq
%

%
%cites from computing
%

\bibitem{spade_icecube} IceCube Data Movement, \url{https://icecube.wisc.edu/science/data/datamovement}.

\bibitem{spade_dayabay}"Data processing and storage in the Daya Bay Reactor Antineutrino Experiment" M. He, Nucl. Phys. B Proceedings Supplement 00 (2015) 1–5 (\url{http://arxiv.org/pdf/1501.06969.pdf}).

\bibitem{atlas_express} "Prompt reconstruction of LHC collision data with the ATLAS reconstruction software" N.Barlow et al, \textit{Journal of Physics: Conference Series 331 (2011) 032004}

%
%cites from nuplatform
%
 
%
%cites from organ
%
\bibitem{LBNEorg} LBNE doc-db~\#6547; \url{http://lbne2-docdb.fnal.gov/cgi-bin/ShowDocument?docid=6547}

%
%cites from summary
%


\end{thebibliography}
